Adaptive Disk Storage for Interaction Graphs

### 2014-03-25 notes/graph-adapt/main.tex
added rdk notes

>>>>

\emph{In the problem you're describing, one natural idea that springs to mind is
  to reduce it back to a graph problem by the edges of the original interaction
  graph as vertices of an "augmented interaction graph" whose vertex set
  consists of both the vertices and edges of the original graph, i.e. all
  entities that might have data associated to them. And two vertices of the
  augmented interaction graph are joined by an edge if either (a) both of them
  are vertices of the original interaction graph, and they are joined by an
  edge, or (b) one is an edge and the other is a vertex which is an endpoint of
  that edge. Pictorially, the augmented interaction graph is obtained by
  inserting a new vertex alongside each edge of the original interaction graph
  and turning the edge into a triangle with the new vertex as its third
  corner. It seems that this would work well assuming that queries which
  traverse an edge are likely to traverse its endpoints. -- rdk}
